Capstone Movielens Report

### 2025-12-09 reports/capstone-movielens.site/05.appendix.Rmd
Fix for functions: mse, mse.cv.

Calculates *Mean Squared Error* as described in [Section 24.1 *Case study: recommendation systems / Loss function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook (New Edition)_[@IDS2_24-1_LF].

@@

::: { #func.mse.args.r .sidebar }
  - **r:** Numeric vector representing a set of residuals as described in [Section 24.1 *Case study: recommendation systems / Loss function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook (New Edition)_[@IDS2_24-1_LF].

@@

Calculates the average value of the *Mean Squared Errors* calculated with the use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6].

>>>>

Calculates *Mean Squared Error* of the set of *residuals* (passed in the [r](func.mse.args.r) argument) as described in [Section 24.1 *Case study: recommendation systems / Loss function*](https://rafalab.dfci.harvard.edu/dsbook-part-2/highdim/regularization.html#sec-netflix-loss-function) of the _Course Textbook (New Edition)_[@IDS2_24-1_LF].

@@

::: { #func.mse.args.r .sidebar }
  - **r:** Numeric vector representing a set of *residuals*.

@@

Calculates the average value of the *Mean Squared Errors* calculated with the use of *K-Fold Cross-Validation* as described in [Section 29.6 *Cross validation / K-fold cross validation*](https://rafalab.dfci.harvard.edu/dsbook-part-2/ml/resampling-methods.html#k-fold-cross-validation) of the _Course Textbook (New Edition)_[@IDS2_29-6_KFCV].
